MixEth: efficient trustless coin mixing service for Ethereum

### 2018-11-10 article/main.tex
Möbius added to related work

		\toprule
		\hline
		&\multicolumn{3}{c}{Anonimity against}& \multicolumn{2}{c}{Availability}&Theft prevention\\
		\cline{2-4}\cline{5-6}&outsiders&senders&recipients&sender&tumbler\\
		\hline
		\midrule
		\textbf{Centralized} & & \\
		\midrule
		Mixcoin \cite{bonneau2014mixcoin} & TTP       & \xmark  &\cmark&\cmark&\xmark&TTP      \\
		Blindcoin \cite{valenta2015blindcoin} & \cmark &\xmark&\cmark&\cmark&\xmark&TTP        \\
		TumbleBit \cite{heilman2017tumblebit} & \cmark &\cmark&\cmark&\cmark&\xmark&\cmark       \\
		\midrule
		\textbf{Decentralized}      &    &      \\
		\midrule
		Coinjoin \cite{maxwell2013coinjoin} & \cmark   &\xmark&\cmark&\xmark&n.a.&\cmark       \\
		Coinshuffle \cite{ruffing2014coinshuffle} & \cmark&\xmark&\cmark&\xmark&n.a.&\cmark       \\
		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\cmark        \\
		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
		\bottomrule
	\end{tabular}
	\label{table:securityproperties}
\end{table}

@@

\section{Related work}
Miximus is a trustless zkSNARK-based mixer for Ethereum. It uses zkSNAKRKs to conceal the mapping between depositors and recipients. A depositor creates a leaf in a Merkle-tree. A depositor needs to exchange the preimage of the leaf with the recipient. Later, a recipient could prove to the Miximus contract that they know one of the preimages of a certain, undisclosed leaf. So called nullifiers enable recipients to withdraw funds once and only once. The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants. However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction. Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK. If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer. Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.

As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$. In spite of this seemingly added complexity, we are confident that these 3 (deposit, shuffle, withdraw) transactions consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus. 
\begin{table}[H] 
\caption{Number of on-chain transactions and off-chain messages required to run a certain coin mixer protocol.}
\centering 
\begin{tabular}{lcc}

>>>>

		\toprule
		\hline
		&\multicolumn{3}{c}{Anonimity against}& \multicolumn{2}{c}{Availability}&Theft prevention\\
		\cline{2-4}\cline{5-6}&outsiders&senders&recipients&sender&tumbler\\
		\hline
		\midrule
		\textbf{Centralized} & & \\
		\midrule
		Mixcoin \cite{bonneau2014mixcoin} & TTP       & \xmark  &\cmark&\cmark&\xmark&TTP      \\
		Blindcoin \cite{valenta2015blindcoin} & \cmark &\xmark&\cmark&\cmark&\xmark&TTP        \\
		TumbleBit \cite{heilman2017tumblebit} & \cmark &\cmark&\cmark&\cmark&\xmark&\cmark       \\
		\midrule
		\textbf{Decentralized}      &    &      \\
		\midrule
		Coinjoin \cite{maxwell2013coinjoin} & \cmark   &\xmark&\cmark&\xmark&n.a.&\cmark       \\
		Coinshuffle \cite{ruffing2014coinshuffle} & \cmark&\xmark&\cmark&\xmark&n.a.&\cmark       \\
		XIM \cite{bissias2014sybil} & \cmark      &\xmark&\cmark&\cmark&n.a.&\cmark       \\
		Möbius \cite{meiklejohn2018mobius}     &\cmark&\cmark&\xmark&\cmark&\cmark&\xmark        \\
		Miximus \cite{miximus2018}&\cmark&\xmark&\xmark&\cmark&\cmark&\cmark  \\
		MixEth&\cmark&\cmark&\xmark&\cmark&\cmark&\cmark  \\
		\bottomrule
	\end{tabular}
	\label{table:securityproperties}
\end{table}

@@

\section{Related work}
Möbius was the very first trustless coin mixer designed for Ethereum\cite{meiklejohn2018mobius}. Authors of Möbius provided formal definitions of various notions of securty such as anonymity, theft prevention and mixer availability. These properties could be used to evaluate and compare existing and future proposals from a security perspective. Möbius is a ring-signature-based trustless coin mixer with minimal on-chain transaction complexity: users of Möbius just need to create a deposit and a withdraw transaction. However the gas cost of the withdrawal transaction increases linearly in the number of receivers, which limits the size of possible anonymity sets. No more than 24 reciever could use Möbius with current cca.$\num[group-separator={,}]{8000000}$  block gas limit. If more people tries to use the mixer funds would be stucked in the mixer contract, since the gas costs of withdrawal transactions would be greater than the block gas limit. Another, maybe even more severe problem with Möbius is that withdrawal transactions can be frontrunned by anyone in the network, meaning that anyone could steal receivers' funds from the Möbius smart contract. When an honest receiver broadcasts a Möbius withdrawal transaction, other peers in the network might just create another withdrawal transaction with the very same valid linkable ring signature but with a considerably larger gas price and with their own address as recipient. Miners will act rationally and pick the transaction with the higher gas price, therefore theft-prevention in Möbius is not guaranteed.

Miximus is a trustless zkSNARK-based mixer for Ethereum\cite{miximus2018}. It uses zkSNARKs to conceal the mapping between depositors and recipients. A depositor creates a leaf in a Merkle-tree. A depositor needs to exchange the preimage of the leaf with the recipient. Later, a recipient could prove to the Miximus contract that they know one of the preimages of a certain, undisclosed leaf. So called nullifiers enable recipients to withdraw funds once and only once. The gas costs of depositing and withdrawing funds from a Miximus mixer is independent of the number of participants. However there are disadvantages of this approach; Miximus only provides anonymity against outsiders, since if Alice funds to Bob via Miximus, Alice will know when Bob made the withdrawal transaction. Another, more severe limitation of Miximus is the trusted setup required for generating the proving key for the zkSNARK. If this trusted setup is compromised, the deployer of the contract, who generated the proving key could potentially steal funds from the mixer. Although, this issue could be amended somehow via a multi-party computation (MPC) further increasing the off-chain communication complexitiy of Miximus.

As Table \ref{table:communicationcomplexity} demonstrates, both Möbius and Miximus require $2$ on-chain transactions, while MixEth requires $3$. In spite of this seemingly added complexity, we are confident that these 3 (deposit, shuffle, withdraw) transactions consume significantly less gas than those (deposit, verify linkable ring signature/zkSNARK) of Möbius and Miximus. 
\begin{table}[H] 
\caption{Number of on-chain transactions and off-chain messages required to run a certain coin mixer protocol. Note that in case of Miximus if one wants to avoid the trusted setup for the zkSNARK, then they need to perform a secure multi-party computation protocol to trust-minimize the proving key generation.}
\centering 
\begin{tabular}{lcc}
